%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[utf8]{inputenc}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}

\usepackage[left=0.75in,top=0.75in,right=0.75in,bottom=0.75in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Nicolás Varela García} % Your name
%\address{Avda. Oporto, Nº 24 - 2º H, 28019, Madrid} % Your address
\address{18.2.A.01 \\ C. Madrid, 139, Getafe, 28903, Madrid} % Your secondary addess (optional)
\address{%(+34)699338741 \\ 
	nicolas.varela@uc3m.es \\ ORCID: 0000-0002-9135-5338 \\ \href{https://nicolobo.github.io/}{Personal webpage}} % Your phone number and email

\usepackage{microtype}
\usepackage{enumitem}


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\vspace{0em}

\begin{rSection}{Education}
	{\bf PhD in Economic History} \hfill {\em 2021 -  $\dots$} 
	\\ Universidad Carlos III de Madrid
	\\ Thesis (provisional): \textit{Monetary policy and political economy during the Francoist regime. A quantitative approach.} Advisor: Stefano Battilossi.
	\\
	\\{\bf Master in Social Sciences} \hfill {\em 2019 - 2021} 
	\\ Universidad Carlos III de Madrid %\hfill {GPA: 8.33}
	%\\ Faculty: Robert Fishman, Ian Shapiro, Stefan Houpt...
	\\ Master's thesis: \textit{Was Spanish inflation always a monetary phenomenon? Evidence from wavelet and SVAR analyses, 1868-1998.} Advisor: Stefano Battilossi. Dissertation Committee: Jordi Domènech, Emiliano Travieso. \\
	\\{\bf Master in Economics} \hfill {\em 2018 - 2019} 
	\\ Universidad Carlos III de Madrid %\hfill {GPA: 7.64}
	%\\Faculty: Álvaro Escribano, Diego Moreno, Andrés Erosa...
	\\ Master's thesis: \textit{Gentrification: culture and crime in urban housing renovation.} Advisor: Álvaro Name-Correa. Dissertation Committee: José Luís Ferreira, Antonia Díaz, Julio Cáceres.
	\\
	\\{\bf Bachelor in Economics} \hfill {\em 2014 - 2018} 
	\\ Universidad de Santiago de Compostela %\hfill {GPA: 8.1263}
	\\ Honors: Mathematics for Economists, Commercial Law, Microeconomics, Regional and Local Development, Fiscal Federalism, Management and Public Government, History of Economic Thought.
	%\\Faculty: Xaime Barreiro, Edelmiro López, Miguel Pérez-Nievas...
	\\ Graduate thesis: \textit{La crisis fiscal de las ciudades. Una aproximación teórica.} Advisor: Luis Caramés.
	%Minor in Linguistics \smallskip \\
	%Member of Eta Kappa Nu \\
	%Member of Upsilon Pi Epsilon \\
\end{rSection}

\vspace{2em}

\begin{rSection}{Academic and Work Experience}
	{\bf Predoctoral fellow - Universidad Carlos III de Madrid} \hfill {\em Feb 2022 - $\cdots$} \\ 
	PIPF UC3M 02-2122 program. \\
	\\{\bf Research Assistant - Universidad Carlos III de Madrid} \hfill {\em Nov 2021 - Jan 2022} \\ Research project: \textit{Desarrollo de los mercados financieros españoles en el siglo XX}, 2019/00368/001. \\ PI: Stefano Battilossi. \\
	\\{\bf Servicio Galego de Saúde (SERGAS)} \hfill {\em June 2017} \\ 
	{\em Technician} \\
	Curricular internship in the Servicio de Coordinación de Servicios Generales.  Implementation of public contracts, labour management and accounting.\\
	\\ {\bf Professional musician} \\
	Performance as soloist and guest of numerous ensembles at national and international venues (World Music Contest, Kerkrade; Jungfrau Music Festival, Interlaken; Festival Rio Loco, Toulouse). Participation in a dozen \mbox{recordings}. 
\end{rSection}

\vspace{2em}	

\begin{rSection}{Teaching}
	{\bf Cooperation, collective action, and formal models of strategy} - Game Theory \hfill {\em 2022-2023} \\
	Dual Bachelors in International Studies + Business Management, IS + Law, IS + Political Science; Bachelor in International Studies (English). \\ 
	\\{\bf The Process of European Economic Integration}	 \hfill {\em 2021-2022} \\
	Bachelor in Economics (English) and Grado en Economía (Spanish, with Teaching Excellent Acknowledgment). \\
	\\{\bf Well-being Measurement, Inequality and Poverty} \hfill {\em 2021-2022} \\
	Master in Economic Development and Growth (MEDEG), tutoring. \\
	\\{\bf Econometrics I} - Time series \hfill {\em 2021-2022} \\
	MEDEG. \\	
	\\{\bf Introductory Econometrics} - Linear regression analysis \hfill {\em 2021-2022} \\
	MEDEG. \\
\end{rSection}	

\vspace{2em}

\begin{rSection}{Other Academic Education}
	{\bf Natural Language Processing with Python} \hfill {\em 2022}
	\\ Udemy. Instructor: Jose Portilla \\
	\\{\bf Academic Writing in English} \hfill {\em 2021}
	\\ UC3M Doctoral School (cross-curricular). Prof. Eoin Higgins \\
	\\{\bf Macroeconomic Diagnostics} \hfill {\em 2021}
	\\ IMFx. Staff: Evan Tanner, Adolfo Barajas, Mikhail Pranovich, Maksym Ivanyna (IMF) \\
	\\{\bf Professional Music Degree }\hfill {\em 2016-2021}\\
	Specialization: Pipe organ (End-of-Career Prize, with Honors, Conservatorio Prof. de Música de Ourense)\\
	\\ {\bf Python Basics for Data Science} \hfill {\em 2020} 
	\\ IBM (through edX). Prof. Joseph Santarcangelo (Data Scientist at IBM) \\
	\\ {\bf Data Science: R Basics} \hfill {\em 2020}
	\\ HarvardX. Prof. Rafael Irizarry (Harvard T.H. Chan School of Public Health) \\
	\\{\bf Course "Pedro Schwartz. El liberalismo, una filosofía en peligro."}\hfill {\em 2018}\\
	Escuela en Red Rafael del Pino. Prof. Pedro Schwartz, OBE (UCM, UAM, UCJC, Mont Pèlerin Society)\\
	\\ {\bf Curso avanzado de formación en competencias en información} \hfill {\em 2017}
	\\Universidad de Santiago de Compostela\\
	\\{\bf Professional Music Degree}\hfill {\em 2008-2014}\\
	Specialization: Percussion (End-of-Career Prize, Conservatorio Profesional de Música de Lalín)
\end{rSection}

\vspace{2em}
\newpage

\begin{rSection}{Grants \& scolarships}
	{\bf Comisión Nacional de los Mercados y la Competencia (CNMC) - DECLINED} \hfill {\em 2021-2022} \\ 
	12-months training fellowship. Declined due to incompatibility with RA position. \\
	\\{\bf UC3M School of Graduate Studies} \hfill {\em 2019-2021} \\ Scholarship %(out of 3 offered)
	to pay tuition fee of the Master in Social Sciences (extended). \\ 
	\\{\bf Government of Spain - Ministry of Education and Vocational Training} \hfill {\em 2018-2019} \\ General Grant for studies of post-secondary level (Master in Economics).\\ With supplement of Academic Excellence.\\
	\\{\bf Government of Spain - Ministry of Education and Vocational Training} \hfill {\em 2014-2018} \\ General Grant for studies of post-secondary level (Bachelor's Degree in Economics).\\
	\\{\bf Government of Spain - Ministry of Education, Culture and Sports} \hfill {\em 2010-2014}\\
	General Grant for studies of post-compulsory and higher non-university level (Music degree).
\end{rSection}

\vspace{2mm}

%\newpage

\begin{rSection}{Publications}
	{\bf Chapters in books}\hfill \\
	"Central banks" in Hsu, Sara (Ed.). \textit{Encyclopedia of Financial Crises}. Edward Elgar Publishing (forthcoming). \\
	\\ "Inflation" in Hsu, Sara (Ed.). \textit{Encyclopedia of Financial Crises}. Edward Elgar Publishing (\mbox{forthcoming}). \\

\end{rSection}

\begin{rSection}{Presentations at conferences}
	{\bf Doctoral Workshop, PhD program in Economic History}\hfill {\em 13/XII/2021}\\
	Universidad Carlos III de Madrid. Presentation \textit{"Monetary policy and political economy in the Francoist regime. A quantitative approach."}\\
\end{rSection}

\vspace{3mm}
%\newpage 

\begin{rSection}{Technical Strengths \& Languages}
	\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
		Statistical software  & Stata, EViews \\
		Programming languages & R, Python \\
		Software \& Tools & \LaTeX, MSFT Office, GitHub \\ 
		\\ Mother tongues & Galician \& Spanish \\
		Other languages & English (advanced - C1) \\ & Italian (basic - A2) \\ & Portuguese (basic)
	\end{tabular}
\end{rSection}

\vspace{3mm}		

\begin{rSection}{Other personal information} \itemsep -3pt
	\item Winner of the Intercampus22 race, Teaching and Research Academic staff category, 5 km \hfill {\em 2022}
	%\item End-of-Career Prize in Music by Conservatorio Profesional de Música de Ourense \hfill {\em 2021}
	\item Valedictorian at Bachelor in Economics Graduation Ceremony \hfill {\em 2018}
	\item Nominee for Extraordinary Prize of Bachelor's Degree \hfill {\em 2018}
	%\item End-of-Career Prize in Music by Conservatorio Profesional de Música de Lalín \hfill {\em 2014}
	\item {Exchange program at Lycée René Descartes (Rennes, France)} \hfill {\em 2011}
	%\item Running PB: 5 km - 23'47''. %Official 24'58''.
	%		\item Co-Organized “ Nirmitee 2017” - a National Symposium of Civil Department of MIT, Pune
	%		\item Attended a workshop on Autodesk Revit at IIT Bombay in 2014.
	%		\item Winner of Inter Departmental Football Competition 2015.
	%		\item Member of the  Rotaract Club Of Pune Pride from 2014 to 2017.
	%		\item Worked for a start-up company Named OUST as a Regional Marketing Manager
	%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
	%\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
	%\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
	%\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %
	
\end{rSection}

%	\begin{rSection}{Personal Traits}
	%		\item Highly motivated and eager to learn new things.
	%		\item Strong motivational and leadership skills.
	%		\item Ability to work as an individual as well as in group.
	%	\end{rSection}
\end{document}